---
title: "report"
author: "Fidisoa Rasambainarivo"
date: "11/2/2021"
output: word_document
---

```{r setup, echo=FALSE}

library(ggplot2)
library(dplyr)
library(sf)
library(zoo)

data<-read.csv("dataset1.csv")
data$date<-as.Date(data$date)
data<-arrange(data,date)
data$dob<-as.Date(data$dob)

```

## Introduction

Ceci est un document préliminaire produit à partir des données de  `r length(data$date)` confirmés par laboratoire et identifiés à Madagascar entre **`r first(na.omit(data$date))`**  et **`r last(na.omit(data$date))`**.

## Statistiques descriptives


Le tableau suivant montre la moyenne d'age par sexe des cas confirmes


```{r, echo=FALSE}

sexe<-data%>%
  group_by(sexe)%>%
  summarise(n=n(),
            "Moyenne age"=mean(age,na.rm = TRUE))

```

## Including Plots

La figure suivante présente l’évolution du nombre de prélèvements positifs  par jour à Madagascar.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r pressure, echo=FALSE}

day<-data%>%group_by(date)%>%
  summarise(cases=n())%>%
  mutate(rollmean=rollmeanr(cases,7,fill=NA))

ggplot(day,aes(x=date,y=cases))+
  geom_col()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
